%-------------------------
% Resume in Latex
% Author: Matty
% Based on: https://github.com/jakegut/resume (which was based on https://github.com/sb2nov/resume)
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{multicol} % Include the multicol package
\usepackage{geometry}

\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section Formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\vspace{-7pt}

\begin{center}
    \textbf{\Huge \scshape Ali Imangholi} \\ \vspace{8pt}
    \small
    \faIcon{globe}
    \href{https://ali-imangholi.github.io}
    {\underline{https://ali-imangholi.github.io}} $  $
    \faIcon{envelope}
    \href{mailto:imangholiali2000@gmail.com}
    {\underline{imangholiali2000@gmail.com}}
    \faIcon{github}
    \href{https://github.com/Ali-Imangholi}{\underline{https://github.com/Ali-Imangholi}} $  $
\end{center}

% -------------------- SUMMARY -----------------------
\section{Summary}
I am Ali Imangholi, a research assistant at the University of Tehran, specializing in efficient and reliable embedded systems and exploring the intersection of Machine Learning algorithms and digital systems.
% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {University of Tehran, Tehran, Iran (\href{https://www.topuniversities.com/university-rankings/world-university-rankings/2024?\&countries=ir}{\textit{\underline{ranked 2\textsuperscript{nd} in Iran}}})}{Sep. 2018 - July 2023}
      {B.Sc. in Electrical Engineering (Digital Systems)}{}
        \resumeItemListStart
            \resumeItem{CGPA: 17.11/20 (3.39/4.0)}
            \resumeItem{GPA (last 71 course credits): 3.66 }
	\resumeItem{Thesis: Hardware Trojan Detection Using Machine Learning Algorithms}
	\resumeItem{Advisor: Prof. Siamak Mohammadi (Associate Professor)}
        \resumeItemListEnd

    \resumeSubheading
      {Nemooneh Dolati Shahid Faraj, Tehran, Iran}{Sep. 2014 - June 2016}
      {Diploma in Mathematics and Physics’ Discipline}{}
        \resumeItemListStart
            \resumeItem{CGPA: 18.68/20}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

% -------------------- RESEARCH INTERESTS --------------------
\section{research interests}
	\begin{multicols}{2}
	\begin{itemize}
		\item Embedded Systems
		\item Reconfigurable computing and FPGAs
		\item ASIC design
		\item Computer architecture
		\item Hardware Trust
		\item IoT Devices
		\item Hardware accelerators
		\item Machine Learning
	\end{itemize}
	\end{multicols}
% -------------------- HONORS and AWARDS -----------------------
\section{Honors and Awards}
\begin{itemize}
    \item Excellent student at the University of Tehran for six semesters (GPA\textgreater{}17/20)
    \item FOE award recipient from the University of Tehran (2\textsuperscript{nd} rank by the end of the first two semesters)
    \item Full Scholarship from the University of Tehran (Tuition Fee)
    \item Receive excellent grade on Bachelor's final project (20/20 (4/4))
\end{itemize}
% -------------------- PUBLICATIONS --------------------
\section{Publications}
\begin{itemize}
    \item \textbf{A. Imangholi}*, M. Hashemi*, A. Momeni, S. Mohammadi and T.E. Carlson. FAST-GO: Fast, Accurate, and Scalable Hardware Trojan Detection using Graph Convolutional Networks. IEEE International Symposium on Hardware Oriented Security and Trust (HOST), 2024 (submitted) \\ (* equal contribution)
\end{itemize}

% -------------------- ACADEMIC EXPERIENCES --------------------
\section{Academic Experiences}
 \resumeSubHeadingListStart
  
    \resumeSubheading
      {Research Assistant}{}
      {Dependable Systems Design Lab (DSD Lab), Tehran, Iran}{July 2022 - Present}
        \resumeItemListStart
        \resumeItem{Supervisor: Prof. Siamak Mohammadi (Associate Professor)}
	\resumeItem{employing a machine learning-based technique to detect Hardware Trojan at gate-level netlists}
        \resumeItem{a research paper has been submitted based on the achieved results}
        \resumeItemListEnd

     \textbf{Teaching Assistant}
	\begin{itemize}
    	\item \emph{Electrical Circuits I, \textbf{Chief TA} \hfill {Jan 2023 - July 2023}}
  		\begin{itemize}
    		\item Instructor: Prof. Shaghayegh Vahdat (Assistant Professor)
  		\end{itemize}
    	\item \emph{Core-based Embedded System Design, \textbf{Chief TA} \hfill {Jan 2023 - July 2023}}
  		\begin{itemize}
    		\item Instructor: Prof. Ahmad Shabani (Ph.D.)
  		\end{itemize}
	\item \emph{Digital Systems Laboratory II, \textbf{Lab TA} \hfill {Jan 2023 - July 2023}}
  		\begin{itemize}
    		\item Instructor: Prof. Saeed Safari (Associate Professor)
  		\end{itemize}
	\item \emph{Electronic System Level Design, \textbf{TA} \hfill {Jan 2022 - July 2022 \& Jan 2023 - July 2023}}
  		\begin{itemize}
    		\item Instructor: Prof. Bijan Alizadehmalafeh (Associate Professor)
  		\end{itemize}
	\item \emph{FPGA-Based Embedded System Design, \textbf{TA/Lab TA} \hfill {Sep. 2022 - Jan. 2023}}
  		\begin{itemize}
    		\item Instructor: Prof. Bijan Alizadehmalafeh (Associate Professor)
  		\end{itemize}
	\item \emph{Electrical Measurement, \textbf{Chief TA } \hfill {Jan 2022 - July 2022}}
  		\begin{itemize}
    		\item Instructor: Prof. Amir Abbas Shaygani Akmal (Associate Professor)
  		\end{itemize}
	\end{itemize}



  \resumeSubHeadingListEnd
% -------------------- SELECTED COURSES --------------------
\section{Selected Courses}
	\begin{multicols}{2}
	\begin{itemize}
		\item Core-based Embedded System Design \\ \textit{Grade: 20/20 (4/4)}
		\item Digital Electronics Circuit \\ \textit{Grade: 20/20 (4/4)}
		\item FPGA-Based Embedded System Design \\ \textit{Grade: 18.1/20 (4/4)} 
		\item Digital Systems II \\ \textit{Grade: 17.5/20 (4/4)}
		\item Digital Systems Laboratory II \\ \textit{Grade: 19.6/20 (4/4)}
		\item Foundations of Information Technology \\ \textit{Grade: 20/20 (4/4)} 
		\item Advanced Programming \\ \textit{Grade: 17.5/20 (4/4)}
		\item Discrete Mathematics \\ \textit{Grade: 19.55/20 (4/4)}
		\item Numerical Computation \\ \textit{Grade: 20/20 (4/4)}
		\item Linear Control Systems \\ \textit{Grade: 20/20 (4/4)}

	\end{itemize}
	\end{multicols}
% -------------------- SOFTWARE ----------------
\section{Software}
Software Programming Languages: MATLAB, C++, Python\\
Hardware Programming Languages: Verilog HDL, System Veriolg HDL\\
Simulators: Modelsim, Quartus, Simulink, PSPICE, HSPICE, LTSPICE\\
Tools: L-Edit, S-Edit\\
OS: Unix-based OS, Microsoft Windows\\
Applications: Microsoft Word, PowerPoint, Excel\\

% -------------------- SELECTED PROJECTS --------------------
\section{Selected Projects}
\begin{itemize}
    \item ARM Processor: Design and Implementation on Cyclone V FPGA\\ \textit{Programing Language: Verilog} \\ \textit{Advisor: Prof. Saeed Safari(Associate Professor)}
    \item UART and SPI Communication Protocols: Design and Implementation on Cyclone V FPGA \\ \textit{Programing Language: Verilog} \\ \textit{Advisors: Prof. Bijan Alizadeh(Associate Professor) \& Prof. Ahmad Shabani(Ph.D.)}
    \item FIR Filter: Design and Implementation on Cyclone V FPGA \\ \textit{Programing Language: Verilog} \\ \textit{Advisor: Prof. Bijan Alizadeh(Associate Professor)}
    \item Gate-Level Simulator: Design \\ \textit{Programing Language: C++}  \\ \textit{Advisor: Prof. Zainalabedin Navabi(Professor)}
    \item More projects are available on  \href{https://ali-imangholi.github.io}{\textit{\underline{my personal website}}}. 
\end{itemize}

% -------------------- MEMBERSHIPS ----------------
\section{Memberships}
\begin{itemize}
\item volunteer member of the International Red Cross and Red Crescent Movement
\end{itemize}

% -------------------- LANGUAGE ----------------
\section{Language}
\begin{itemize}
\item Persian: Native
\item English: Proficient (IELTS exam will have been taken by Nov. 15, 2023)
\end{itemize}

% -------------------- REFERENCES ----------------
\section{References}
\begin{itemize}
\item Will be available upon request
\end{itemize}
%--------------------------------------------------------------------------
\end{document}
